The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-08 paper/sections/related.tex
oh boy that was a rough paragraph...

>>>>

\revise{
\emph{Embedded Methods} are a popular technique in computer graphics in which complex geometry is embedded in a coarse mesh that guides the simulation. The early work of ~\cite{10.5555/1009379.1009573} proposed a method for volumetric simulation of surface meshes by embedding the surface in a background cubic mesh may be seen as an alternative strategy to ours. However, producing an embedded mesh introduces a number of challenges since the coarse mesh's topology must mirror that of the embedded surface, which necessitates complex hierarchical methods like that of ~\cite{10.1145/1531326.1531358}. Also like in IGA methods, many methods rely on cut cells to conform to the boundary, requiring complicated geometric operations. Furthermore when the DOFs do not lie on the boundary, complex methods such as Nitsche's Method ~\cite{Nitsche1971berEV} are required for handling Dirichlet boundary conditions. By making use of an entirely meshless pipeline and operating directly on the input curves, we avoid much of these difficulties in embedded methods.
}
